Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-24 paper.tex
Transport looks at streamwise momentum
Add info to transport total fig caption

 \caption{Normalized momentum transport quantities computed as weighted
 averages from Equation~(\ref{eq:momentum}).}

@@

    \caption{Normalized transport totals from Figures~\ref{fig:mom-bar-graph}
        and \ref{fig:K-bar-graph} plotted \textit{versus} the Reynolds number.}

>>>>

 \caption{Normalized streamwise momentum transport quantities computed as
     weighted averages from Equation~(\ref{eq:momentum}).}

@@

    \caption{Normalized transport totals from Figures~\ref{fig:mom-bar-graph}
        (streamwise momentum, $U$) and \ref{fig:K-bar-graph} (mean kinetic energy,
        $K$) plotted \textit{versus} the Reynolds number.}
